Extended Data

### 2021-12-03 doc/manuscript/Dow_manuscript_Nature.Rmd
draft code availability statement
@camerondow35 , could you please add version numbers for the R packages we used and add any I missed?

<!--QUILT PLOT METHODS-->
For the analysis of correlation between RWI and climate variables, we obtained monthly $T_{max}$ and $T_{min}$ data for 1901-2019 from CRU v.4.04 [@harris_version_2020].
Correlations between monthly climate and $RWI$ were assessed using ‘dplR’[@bunn_dendrochronology_2008] and ‘bootRes’[@zang_dendroclimatic_2013] in R v 4.0 (R Core Team, 2020), which correlated functions and bootstrapped confidence intervals for these relationships[@biondi_dendroclim2002_2004].
We analyzed these correlations for January through September of the current year (presented in Fig. `r tree_rings`, `r EDF_tree_rings_TMIN`).
To test for potential lag effects of spring temperatures on growth the following year, we also ran a version of the analysis extending back to include climate of every month of the previous year (`r EDF_tree_rings_TMAX_extended`).
Correlations and significance levels for months April-August are given in `r chron_table`.

@@

# Code Availability Statement {-#Code}

>>>>

<!--QUILT PLOT METHODS-->
For the analysis of correlation between RWI and climate variables, we obtained monthly $T_{max}$ and $T_{min}$ data for 1901-2019 from CRU v.4.04 [@harris_version_2020].
Correlations between monthly climate and $RWI$ were assessed using *dplR*[@bunn_dendrochronology_2008] and *bootRes*[@zang_dendroclimatic_2013] in R v 4.0 (R Core Team, 2020), which correlated functions and bootstrapped confidence intervals for these relationships[@biondi_dendroclim2002_2004].
We analyzed these correlations for January through September of the current year (presented in Fig. `r tree_rings`, `r EDF_tree_rings_TMIN`).
To test for potential lag effects of spring temperatures on growth the following year, we also ran a version of the analysis extending back to include climate of every month of the previous year (`r EDF_tree_rings_TMAX_extended`).
Correlations and significance levels for months April-August are given in `r chron_table`.

@@

# Code Availability Statement {-#Code}
Data were analysed in the open source statistical software R (version 4.0).
We used packages *Rdendrom* (https://github.com/seanmcm/RDendrom/), *climwin* v.1.2.3 (https://cran.r-project.org/web/packages/climwin/index.html), *climpact* (see www.climpact-sci.org)[@benestad_empiricalstatistical_2008], *dplR* **version###**, and *bootRes* **version###**. 
All custom code is available through the EcoClimlab GitHub repository (https://github.com/EcoClimLab/growth_phenology) and archived in Zenodo (DOI: TBD).
